Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-08 ongoing/report/sec_1_introduction.tex
Work on Main Bound

To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(x(t)\) is random instances of i.i.d.\ Rademacher distribution drawn in each time index, \(h(t)\) is the channel's impulse response, \(y(t)\) as the output, and \(z(t)\) is i.i.d.\ normalized AWGN
Simply assuming \(h\) has sparse support, and let the convolution with \(x\) be expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that \(y =X h +z\).
Then Bajwa et.\ al.\ was able to show that, \(X\) is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

>>>>

To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(h(t)\) is the channel's impulse response, \(y(t)\) is the output, and, for each time index, \(x(t)\) is i.i.d.\ Rademacher, and \(z(t)\) is i.i.d.\ Gaussian.
Simply assuming \(h\) has sparse support, and let the convolution with \(x\) be expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that \(y =X h +z\).
Then Bajwa et.\ al.\ was able to show that, \(X\) is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

### 2019-01-08 ongoing/report/sec_2_problem_setting.tex
Shorten introduction
Work on Main Bound

We restrict our consideration to the uniform linear array, which can be modeled as
%
\Disp{
\V{a} \in \MB{V}_\MB{K} (N_h) \\
\V{a} (\psi')
=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
}
%
where \(\RM{e}\) is the base of natural logarithm, and \(i\) the imaginary unit.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
%
\Disp{
H
=\sum_{l=1}^L \alpha_l \V{a} \left( \frac{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \frac{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
}
%
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
%
\Disp{
\varphi_l
=\frac{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
\vartheta_l
=\frac{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
}
%
to get a simpler form
%
\Disp{
H
=\sum_{l=0}^L \alpha_l \V{a} (\varphi_l) \V{a} (\vartheta_l)^\H
}
%

@@

We consider the hybrid configuration at both transmitter and receiver end.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \(F_B\) and analog precoder \(F_R\).
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \(W_B\) and analog combiner \(W_R\).
To set up notation, we list them as below.
%
\Disp{
\M{F}_B \in &\MB{M}_{\MB{C}} (N_r, N_y) \\
\M{F}_R \in &\MB{M}_{\MB{C}} (N_h, N_r) \\
\M{W}_R \in &\MB{M}_{\MB{C}} (N_r, N_h) \\
\M{W}_B \in &\MB{M}_{\MB{C}} (N_y, N_r).
}
%
Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
%
\Disp{
|\M{F}_R (n_h, n_r)| =&1, \\
|\M{W}_R (n_r, n_h)| =&1, \\
n_h =&1, \dotsc N_h, \NT \\
n_r =&1, \dotsc N_r \NT
}
%
And we assume
\Disp{
N_h \gg &N_r \\
N_r \gg &N_s
}

@@

We may introduce the effective channel
%
\Disp{
Y (\omega_h, \omega_e)
:=W_B (\omega_r) W_R (\omega_r) \Big[ H (\omega_h) F_R (\omega_t) F_B (\omega_t) +Z (\omega_z) \Big]
}
%
Supress the event space index for brevity, we restate the same equation as
%
\Disp{
Y
:=W_B W_R ( H F_R F_B +z )
}
\(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
%
\Disp{
\M{Y} (:,n_y)
:=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \\
\quad n_y &=1, 2, \dotsc, N_y \NT
}
%
Still, the crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control.

@@

If we had followed the widely accepted approach of compressive channel sensing, we would have written
%
\Disp{
\V{h}
:= &\RM{vec} (\M{H})
\in \MB{V}_{\MB{C}} (N_h^2) \\
\V{y}
:= &\RM{vec} (\M{Y})
\in \MB{V}_{\MB{C}} (N_y^2) \\
\V{z}^\star
:= &\RM{vec} (\M{Z})
\in \MB{V}_{\MB{C}} (N_y^2) \\
\M{P}^\star
:= &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
\in \MB{M}_{\MB{C}} (N_y^2, N_h^2).
}
%
to formulate our goal as sparse recovery problem of \(\RM{vec} (H)\) to be
%
\Disp{
\V{y} =\M{P}^\star \V{h} +\V{z}^\star
}
%
But, as we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
What shall we do?

@@

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
%
\Disp{
\M{K} \in &\MB{M}_{\MB{C}} (N_h, N_h) \NT \\
\M{K} (n_1, n_2) =&\frac{1} {\sqrt{N_h}} \RM{e}^{2\pi i n_1 n_2 /N_h}, \\
\quad n_1, n_2 =&0, 1, \dotsc, N_h-1 \NT
}
%
Observe that, if we write
%
\Disp{
\M{G}
=\M{K}^\H \M{H} \M{K}
}
%
which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
%
\Disp{
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
}
%
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.

That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
To simplify notation, set 
%
\Disp{
\M{P}
=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
\in \MB{M}_{\MB{C}} (N_y^2, N_h^2)
}
%
And accordingly
\Disp{
\V{g}
:= &\RM{vec} (\M{G})
\in \MB{M}_{\MB{C}} (N_h^2) \\
\V{z}
:= &\RM{vec} (\M{K}^\H \M{Z})
\in \MB{V}_{\MB{C}} (N_y^2)
}
%
Then
%
\Disp{
\V{y}
=\M{P} \V{g} +\V{z}
}
%
If so, our program reads

\Result
{Program}
{
Let \(\M{P}, \V{y}\) be defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
%
\Disp{
\hat{\V{g}}
=\min_{\V{g}'} \|\V{g}'\|_1 \quad
\RM{subject}\; \RM{to}\quad \|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
}
%
And convert \(\hat{\V{g}}\) back to the space domain as
%
\Disp{
\hat{G} =\RM{vec}^{-1} (\hat{g})
}
%
And finally recover the estimated \(H\) as
%
\Disp{
\hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H.
}
%
}

>>>>

We restrict our consideration to the uniform linear array, which can be modeled as
%
\Disp{
\V{a} \in \MB{V}_\MB{K} (N_H) \\
\V{a} (\psi')
=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
}
%
where \(\RM{e}\) is the base of natural logarithm, and \(i\) the imaginary unit.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
%
\Disp{
H
=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
}
%
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
%
\Disp{
\varphi_l
=\F{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
\vartheta_l
=\F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
}
%
to get a simpler form
%
\Disp{
H
=\sum_{l=0}^L \alpha_l \V{a} (\varphi_l) \V{a} (\vartheta_l)^\H
}
%

@@

We consider the hybrid configuration at both transmitter and receiver end.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \(F_B\) and analog precoder \(F_R\).
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \(W_B\) and analog combiner \(W_R\).
To set up notation, we list them as below.
%
\Disp{
\M{F}_B \in &\MB{M}_{\MB{C}} (N_R, N_Y) \\
\M{F}_R \in &\MB{M}_{\MB{C}} (N_H, N_R) \\
\M{W}_R \in &\MB{M}_{\MB{C}} (N_R, N_H) \\
\M{W}_B \in &\MB{M}_{\MB{C}} (N_Y, N_R).
}
%
Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
%
\Disp{
|\M{F}_R (n_h, n_r)| =&1, \\
|\M{W}_R (n_r, n_h)| =&1, \\
n_h =&1, \dotsc N_H, \NT \\
n_r =&1, \dotsc N_R \NT
}
%
And we assume
\Disp{
N_H \gg &N_R \\
N_R \gg &N_s
}

@@

We may introduce the effective channel
%
\Disp{
Y (\omega_h, \omega_e)
:=W_B (\omega_r) W_R (\omega_r) \Big[ H (\omega_h) F_R (\omega_t) F_B (\omega_t) +Z (\omega_z) \Big]
}
%
Supress the event space index for brevity, we restate the same equation as
%
\Disp{
Y
:=W_B W_R ( H F_R F_B +z )
}
\(\M{Y}\) has \(N_Y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
%
\Disp{
\M{Y} (:,n_y)
:=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \\
\quad n_y &=1, 2, \dotsc, N_Y \NT
}
%
Still, the crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control.

@@

If we had followed the widely accepted approach of compressive channel sensing, we would have written
%
\Disp{
\V{h}
:= &\RM{vec} (\M{H})
\in \MB{V}_{\MB{C}} (N_g) \\
\V{y}
:= &\RM{vec} (\M{Y})
\in \MB{V}_{\MB{C}} (N_y) \\
\V{z}^\star
:= &\RM{vec} (\M{Z})
\in \MB{V}_{\MB{C}} (N_y) \\
\M{P}^\star
:= &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
\in \MB{M}_{\MB{C}} (N_y, N_g).
}
%
to formulate our goal as sparse recovery problem of \(\RM{vec} (H)\) to be
%
\Disp{
\V{y} =\M{P}^\star \V{h} +\V{z}^\star
}
%
But, as we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
What shall we do?

@@

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
%
\Disp{
\M{K} \in &\MB{M}_{\MB{C}} (N_H, N_H) \NT \\
\M{K} (n_1, n_2) =&\F{1} {\sqrt{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
\quad n_1, n_2 =&0, 1, \dotsc, N_H-1 \NT
}
%
Observe that, if we write
%
\Disp{
\M{G}
=\M{K}^\H \M{H} \M{K}
}
%
which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
%
\Disp{
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
}
%
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.

That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
To simplify notation, set
%
\Disp{
\M{P}
=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
\in \MB{M}_{\MB{C}} (N_y, N_g)
}
%
And accordingly
\Disp{
\V{g}
:= &\RM{vec} (\M{G})
\in \MB{M}_{\MB{C}} (N_g) \\
\V{z}
:= &\RM{vec} (\M{K}^\H \M{Z})
\in \MB{V}_{\MB{C}} (N_y)
}
where for short we set
\Disp{
N_g =&N_H^2 \\
N_y =&N_Y^2
}
%
Then
%
\Disp{
\V{y}
=\M{P} \V{g} +\V{z}
}
%
If so, our program reads

\Result
{Program}
{
Let \(\M{P}, \V{y}\) be defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
%
\Disp{
\hat{\V{g}}
=\min_{\V{g}'} &\|\V{g}'\|_1 \quad
\RM{subject}\; \RM{to}\quad &\|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
}
%
And convert \(\hat{\V{g}}\) back to the space domain as
%
\Disp{
\hat{G} =\RM{vec}^{-1} (\hat{g})
}
%
And finally recover the estimated \(H\) as
%
\Disp{
\hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H.
}
%
}

### 2019-01-08 ongoing/report/sec_3_theorems_and_proofs.tex
Work on Main Bound

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
To simplify the exposition, we will continue to use the variables \(\V{P}\), \(\V{g}\), \(\V{y}\), and \(\V{z}\) introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\).
At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.

\subsection{Beamspace Channel is Almost Sparse}

Consider
%
\Disp{
d =g -\hat{g}
}
%
And let
\begin{itemize}
\item \(\MC{A}\) be the largest \(L\) position of \(g\).
\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
\item \(\MC{C} =T(N_h^2) -\MC{B} -\MC{C}\), i.e., the complementary index set.
\end{itemize}
So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
%
\Disp{
\MC{A}, \MC{B}, \MC{C} \subset T(N_h^2) \\
\MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
\MC{A} \cup \MC{B} \cup \MC{C} =T(N_h^2).
}

@@

\Result
{Lemma}
{
Let \(\varphi (\omega_h)\) be uniformly, independently distributed in \([0,2\pi)\), and array response \(\V{a} (\varphi)\) defined as in ().
Then
%
\Disp{
\| \V{a} (\varphi) \|_1
\leq \F{1}{\pi^2} \log \F{L}{N}.
}
%
}

To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
%
\Disp{
D (\varphi')
:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi'} \right| \\ \NT
=&\F{|\sin (N \varphi'/2)|}{|\sin (\varphi' /2)|},
\quad 0 \leq \varphi' \leq \pi
}
%

Recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\left| D (\varphi') \right|
= \F{48}{|\varphi'^2 -24| |\varphi'|}
\quad 0 \leq \varphi' \leq \pi,
}
%
The fraction above can be bounded.

Particularly,
%
\Disp{
\F{1}{N} S \left( \varphi' -\F{2\pi k}{N} \right)
=&\F{1}{N} \left| \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
\leq& \F{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
}
%
where \(\varphi' =k/N -\varphi/2\pi\), and the cubic expression is split.
We wish to bound the tail of \(S (\pi \varphi')\), and apply the na\"ive bound
%
\Disp{
&\F{N}{2\pi} \cdot \F{48}{N \pi^3} \int_{L/N}^1 \F{1}{\varphi'^3 -24 \varphi' /\pi^2}
 d\varphi' \NT \\
=&\F{1}{2\pi^2} \cdot \left( 2 \log \F{L}{N} +\log \F{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
\leq& \F{1}{\pi^2} \log \F{L}{N}
}
%
Here, the integral in the first line is immediate.
The second term in the bracket is smaller than 0 and is dropped in the last inequality.
The proof of Lemma () is complete.

The bound is satisfying enough, though refinement is surely possible.
Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
Intuitively, this says that when there are few paths, but many antennas, we expect the spatial frequency domain of the virtual channel to be sparse too.

@@

@@

From ``Decoding from Linear Programming'',
\Result
{Lemma}
{
%
\Disp{
\leq 
\tau_{s, s'}
\leq \delta_s
}
}

The rest follows ``The Dantzig Selector'' very closely.
\Result
{Proposition}
{
Let \(g\) and \(d\) be defined as above.
Then
%
\Disp{
\|d_{BC}\|_1
\leq \|d_{\MC{A}}\|_1 +\|g_{BC}\|_1
}
}

To show this, observe
%
\Disp{
&\|g\|_1 -\|d_{\MC{A}}\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1 \\
\leq& \|g +d\|_1 \NT \\
\leq& \|g\|_1
}
%
In the first line, we recall \(g =g_{\MC{A}}\).

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
|\IP{ d, P(:, n_h) }|
\leq& 4 \sqrt{\log N_h},
\quad n_h =1, \dotsc, N_h^2.
}
%
}

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \sqrt{\log N_h},
\quad n_h =1, \dotsc, N_h^2.
}
%
}

To show this, start with
%
\Disp{
&\IP{ z -(y -P g), P (:,n_y) } \NT \\
=&\IP{ P \hat{g} -P g, P (:,n_y) } \NT \\
=&\IP{ P g, P (:,n_y) }
}
%
Result follows from triangle inequality, and Lemma ().

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with constant \(\delta\).
%
\Disp{
\|d_{\MC{A}}\|_2
\leq \F{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\F{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
}
%
}

@@

>>>>

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_g}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
To simplify the exposition, we will continue to use the variables \(\V{P}\), \(\V{g}\), \(\V{y}\), and \(\V{z}\) introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(s\).
At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.

\subsection{Almost-Sparsity of Beamspace Channel Matrix}

We apply DS to find \(\hat{g}\), setting
\Disp{
\gamma =\sqrt{2 \log N_g}
}
Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
d =\hat{g} -g
}
%
And call
\begin{itemize}
\item \(\MC{A}\) be the largest \(s\) position of \(g\).
\item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
\item \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
\end{itemize}

@@

\Result
{Definition}
{
For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
\Disp{
\sum_{n=s+1}^N |S(x) (n)|
\leq R.
}
}

\Result
{Lemma (Tentative)}
{
Suppose \(0 \leq \varphi \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
Let \(\varphi\) be given, and array response \(\V{a} (\varphi)\) defined as in ().
Then \(\V{a} (\varphi)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R\)
%
\Disp{
R
\leq 2 N_H \log \F{2\pi N_H}{L}.
}
}

The lemma is the key to estimating sparsity of \(h\), which we now show.
Recall the identity for Dirichlet kernel
%
\Disp{
D (\varphi')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \varphi'} \right| \NT \\
=&\F{|\sin (N_H \varphi'/2)|}{|\sin (\varphi' /2)|},
\quad 0 \leq \varphi' \leq \pi
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\left| D (\varphi') \right|
= \F{48}{|\varphi'^2 -24| |\varphi'|}
\quad 0 \leq \varphi' \leq \pi,
}

Particularly, for arbitrary \(\varphi\), find \(k\) so that
\Disp{
\eta :=&\varphi -\F{2\pi k}{N_H}, \\
\left| \eta \right|
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
K^\H a(\varphi) (k)
=D \left( \varphi -\F{2 \pi k} {N_H} \right)
}
So we need only bound
\Disp{
R(\eta) :=\sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq N_H \int_{\varphi'=2\pi L/N_H}^{2\pi} |D(\varphi')| d \varphi'
}
Bound \(D\) by above technique, meanwhile we notice \(\varphi' <24\).
\Disp{
R(\varphi)
\leq &\F{N_H}{2\pi} \int_{\varphi'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\varphi'^2) \varphi'} d \varphi'
+\F{2\pi} {N_H} \\
=&\F{N_H}{\pi} \log \F{2\pi N_H}{L} -\log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the second log term \(<1\) and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\varphi)
\leq \F{N_H}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\varphi\) and \(\vartheta\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(g\) be defined as above.
Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue
%
\Disp{
R
\leq \F{L N_H^2}{\pi^2} \left( \log \F{N_H}{L} \right)
}
}

@@

From ``Decoding from Linear Programming'' (Cand\`es and Tao 2005), Lemma 1.1:

\Result
{Lemma}
{
Let \(P\) be given.
Then \(\tau_{s, s'}\) is bounded in both direction as follows,
\Disp{
\delta_{s+s'} -\max (\{\delta_s, \delta_{s'}\})
\leq \tau_{s, s'}
\leq \delta_{s+s'}
}
}

Thus \(\delta_s\), which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
We may well keep track of \(\delta_s\) only.

\Result
{Lemma}
{
Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
Then \(P\) is RIP according to \(\delta\) for at least probability
\Disp{
   1 -2 \left( \F{12}{\delta} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\delta}{2} N_p \right]
}
}

@@

The rest follows ``The Dantzig Selector'' very closely.
The generalization to complex vector is necessary (though we will ultimately do it in simulation involving real numbers only.
We spell out the proof when such generalization is nontrivial.

\Result
{Proposition}
{
Let \(g\) and \(d\) be defined as above.
Then
%
\Disp{
\|d_{\MC{C}}\|_1
\leq \|d_{\MC{A}}\|_1 +2\|g_{C}\|_1
}
}

To show this, observe that with triangle inequality applied respectively on \(\MC{A}\) and \(\MC{C}\),
\Disp{
\|g\|_1
-\|d_{\MC{A}}\|_1
+\|d_{\MC{C}}\|_1
-\|g_{\MC{C}}\|_1
\leq \|g+d\|_1
}
In the first line, we recall \(g =g_{\MC{A}}\).
On the other hand, by construction that \(\hat{g}\) minimizes the \(\ell_1\)-norm,
\Disp{
\|g+d\|_1
=\|\hat{g}\|_1
\leq \|g\|_1
}
The result follows by combining.

\Result
{Lemma}
{
Let \(z\) and \(P\) be defined as above.
Then
%
\Disp{
|\IP{ z, P(:, n_g) }|
\leq& 2 \sqrt{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
%
with overwhelming probability.
}

This only depends on the fact that \(P(:, n_g)\) has unity \(\ell_2\)-norm, and on the randomness of \(z\).

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \sqrt{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
}

To show this, by definition
%
\Disp{
&\IP{ z -(y -P \hat{g}), P (:,n_y) } \NT \\
=&\IP{ P \hat{g} -P g, P (:,n_y) } \NT \\
=&\IP{ P d, P (:,n_y) }
}

By construction
\Disp{
\| P (:,n_y)^\H (y -P \hat{g}) \|
\leq &\| P^\H (y -P \hat{g}) \|_\infty \\
\leq &2\sqrt{\log N_g}
}
By triangle inequality, together with lemma (), we have
\Disp{
\|P (:,n_y)^\H P d\|
\leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
\leq &2 \sqrt{\log N_g} +2 \sqrt{\log N_g}
}
which implies
\Disp{
\|P^\H P d\|_\infty
\leq &4 \sqrt{\log N_g}.
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\delta_s\).
%
\Disp{
\|d_{\MC{AB}}\|_2
\leq \F{1}{1-\delta_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\delta_{3s}}{(1-\delta_{2s}) \sqrt{L}} \|d_{C}\|_1
}
%
}

@@

\Result
{Theorem}
{
Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
Then, if \(g\) is almost-\(L\)-sparse with residue \(\epsilon(N,L)\), then
\Disp{
-\|g_{\MC{C}}\|_2
\leq C 4 (\log N_g) \cdot \left( L +\F{1}{L} \epsilon(N,L) \right)
}
with overwhelming probability.
}

\Disp{
\| d \|_2^2
\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \\
\leq \F{1}{(1-\delta_{2s})^2}
\left(
\|P_{\MC{A}\MC{B}}^\Tr P d\|_2^2
+\F{\delta_{3s}^2} {(1-\delta_{2s})^2 L} \|d_{C}\|_1^2
\right)
+\F{1}{L} \|d_{\MC{C}}\|_1^2
}
